Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2019-02-08 pkg/disttree/inst/draft/draft.Rnw
further comments and revisions based on reviews
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2455 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 040ae125f359c8e60b9c8e376d9569c786f4c006

>>>>

\subsubsection*{Distributional complexity / Orthogonality of distribution parameters}
\hlc{Allowing for splits in each distribution parameter rather than only in the location parameter
is particularly advantageous if the parameters are orthogonal, i.e. do not depend on each other,
as changes in parameters other than the location parameter would be overlooked otherwise.
If there is a dependency among parameters it can be sufficient considering only one parameter 
in order to detect all changes, but this depends on the type of dependency.

In the case of the here applied censored Gaussian distribution a shift in the mean also influences 
the variance, hence the parameters are not orthogonal. The same holds for the 
distributions employed in Supplement A} \citep{Schlosser+Hothorn+Stauffer:2018a}. 
\hlc{Therefore, distributional trees and forests have shown to perform reasonably well also for  
distributions with non-orthogonal parameters. However, testing a broader variety of 
distributions, particularly very complex distributions such as the Dagum distribution}
(see, e.g., \cite{Klein+Kneib+Lang:2015}) 
\hlc{are required in order to confirm these findings in general.}
